Viscous Erosion in Porous Media

### 2018-03-13 docs/methods/erosion_methods.tex
NM

>>>>

We further quantify many of these observations in Fig.~\ref{fig:mbodyplots}. First, Fig.~\ref{fig:mbodyplots}(a) shows area fraction versus time. The area fraction is the total area of all bodies as compared to the domain area, i.e.~the 2D counterpart of volume fraction. The initial configuration of 6 circles comprises about 40\% of the domain area, and this percentage steadily decreases as the bodies erode. Figure \ref{fig:mbodyplots}(b) shows the inlet/outlet flow-rate, $\umax$, over time.
